---
title: "Analyses Of LNG Plant Constructions Engineering Deliverables
Progress, Planned & Forecast"
author: "Ashifuddin Mandal & Maryam Mehdipour"
date: "`r Sys.Date()`"
output: slidy_presentation
---

## Important Terms

**Data Analysis** is the process of systematically applying statistical and/or logical techniques to describe and illustrate, condense and recap, and evaluate data.


**Project Management** The use of procedures, techniques, abilities, knowledge, and experience to accomplish certain project goals in accordance with established standards is known as project management.


**Deliverable** Deliverable are basically the products of project activities, which are produced by projects. The size and number of project deliverable might vary depending on the project. During the project planning phase, the project management team and stakeholders come to an arrangement about the specifications of deliverable.


**Weight factor** A weight factor is a numerical value assigned to an element or variable to indicate its relative importance or significance within a larger system or calculation.



## Engineering deliverable progress report

- Communication


- Transparency


- Accountability


- Decision Making


- Performance Evaluation


## Problem & Solution


Within the dynamic organizational structure of the EPC construction contractors
operating on LNG plants. When there are more than 1000 deliverable documents to manage, things get extremely complicated. In order to maintain the project's baseline schedule, it is essential to keep track of any delays and visualize the progress that has been made.


This procedure will define a method for calculating the progress of the engineering work into the various levels in accordance with the scope of the work and the supply. In order to calculate the overall engineering progress.

## Data set
The data set for this project has been taken from TGE Gas Engineering GmbH. We can have a look into the variables of the considered data set below.


```{r}
library(knitr)
library(kableExtra)
library(readxl)
library(dplyr)
dataSet <- read_excel("C:/Users/MandalA/Downloads/project/dataSet.xlsx")
kable(dataSet)
```

## Structure


The structure of this project is divided into four parts, where firstly we arrange the number of monthly progress we need. We have variable of dates for the for Plan , Forecast & Actual. Secondly, we need to get a curve of plan dates according to the months. Thirdly, we need to get a curve of Forecast dates according to the months and finally we need to get a curve of Actual progress. At the end we will marge all the data to analyze the progress and delays.

## Slide with R Output

```{r}
# Importing the required packages 
library(readxl)
library(dplyr) 
```


```{r}
dummydf <- data.frame (date_month  = c("2022-01",
                                  "2022-02",
                                  "2022-03",
                                  "2022-04",
                                  "2022-05",
                                  "2022-06",
                                  "2022-07",
                                  "2022-08",
                                  "2022-09",
                                  "2022-10",
                                  "2022-11",
                                  "2022-12",
                                  "2023-01",
                                  "2023-02",
                                  "2023-03",
                                  "2023-04",
                                  "2023-05",
                                  "2023-06",
                                  "2023-07",
                                  "2023-08",
                                  "2023-09",
                                  "2023-10",
                                  "2023-11",
                                  "2023-12",
                                  "2024-01",
                                  "2024-02",
                                  "2024-03",
                                  "2024-04"
))
```

## reading the excel data file

```{r}
dataSet <- read_excel("C:/Users/MandalA/Downloads/project/dataSet.xlsx")
print(dataSet)
```

## calculating weights

```{r}
dataSet$weight <- round((dataSet$`Man Hours`/sum(dataSet$`Man Hours`))*100, digits = 4)

dataSet$weightIFR <- round((dataSet$`Man Hours`/sum(dataSet$`Man Hours`))*70, digits = 4)

dataSet$weightIFU <- round((dataSet$`Man Hours`/sum(dataSet$`Man Hours`))*30, digits = 4)
```

### calculating weight per discipline

```{r}
dataSet <- dataSet %>%
  group_by(Discipline) %>%
  mutate(WeightPerDiscipline = sum(`Man Hours`))

dataSet$WeightPerDiscipline <- round((dataSet$`Man Hours`/ dataSet$WeightPerDiscipline)*100, digits = 3)
```

## For planned

```{r}
#Aggregating IFR based on month  
dfp_IFR <- aggregate(weightIFR ~ format(as.Date(dataSet$`IFR Planned`) , "%Y-%m") , dataSet , sum )
colnames(dfp_IFR)[1] ="date_month"
```

```{r}
#Aggregating IFU
dfp_IFU <- aggregate(weightIFU ~ format(as.Date(dataSet$`IFU Planned`) , "%Y-%m") , dataSet , sum )
colnames(dfp_IFU)[1] ="date_month"
       
dfp_IFR_IFU <- merge(x=dfp_IFR,y=dfp_IFU, by = c("date_month"),all = TRUE)   
dfp_IFR_IFU[is.na(dfp_IFR_IFU)] <- 0

dfp_IFR_IFU$totalPlaned <- dfp_IFR_IFU$weightIFR+dfp_IFR_IFU$weightIFU 

dfp_IFR_IFU_planned <- merge(x=dummydf,y=dfp_IFR_IFU, by = c("date_month"),all = TRUE)

dfp_IFR_IFU_planned[is.na(dfp_IFR_IFU_planned)] <- 0

dfp_IFR_IFU_planned <- select(dfp_IFR_IFU_planned ,date_month, totalPlaned)

dfp_IFR_IFU_planned <- dfp_IFR_IFU_planned %>%
                      mutate(totalRunningPLan = cumsum(totalPlaned))

dfp_IFR_IFU_planned <- select(dfp_IFR_IFU_planned ,date_month, totalRunningPLan)
```

## For Forecast

```{r}
#Aggregating IFR based on month  
dff_IFR <- aggregate(weightIFR ~ format(as.Date(dataSet$`IFR Forecast`) , "%Y-%m") , dataSet , sum )
colnames(dff_IFR)[1] ="date_month"
```

```{r}
#Aggregating IFU
dff_IFU <- aggregate(weightIFU ~ format(as.Date(dataSet$`IFU Forecast`) , "%Y-%m") , dataSet , sum )
colnames(dff_IFU)[1] ="date_month"

dff_IFR_IFU <- merge(x=dff_IFR,y=dff_IFU, by = c("date_month"),all = TRUE)   
dff_IFR_IFU[is.na(dff_IFR_IFU)] <- 0

dff_IFR_IFU$totalForecast <- dff_IFR_IFU$weightIFR+dff_IFR_IFU$weightIFU 

dff_IFR_IFU_Forecast <- merge(x=dummydf,y=dff_IFR_IFU, by = c("date_month"),all = TRUE)

dff_IFR_IFU_Forecast[is.na(dff_IFR_IFU_Forecast)] <- 0

dff_IFR_IFU_Forecast <- select(dff_IFR_IFU_Forecast ,date_month, totalForecast)

dff_IFR_IFU_Forecast <- dff_IFR_IFU_Forecast %>%
  mutate(totalRunningForecast = cumsum(totalForecast))

dff_IFR_IFU_Forecast <- select(dff_IFR_IFU_Forecast ,date_month, totalRunningForecast)
```

## For Actual

```{r}
#Aggregating IFR based on month  
dfa_IFR <- aggregate(weightIFR ~ format(as.Date(dataSet$`IFR Actual`) , "%Y-%m") , dataSet , sum )
colnames(dfa_IFR)[1] ="date_month"
```

```{r}
#Aggregating IFU
dfa_IFU <- aggregate(weightIFU ~ format(as.Date(dataSet$`IFU Actual`) , "%Y-%m") , dataSet , sum )
colnames(dfa_IFU)[1] ="date_month"

dfa_IFR_IFU <- merge(x=dfa_IFR,y=dfa_IFU, by = c("date_month"),all = TRUE)   
dfa_IFR_IFU[is.na(dfa_IFR_IFU)] <- 0

dfa_IFR_IFU$totalActual <- dfa_IFR_IFU$weightIFR+dfa_IFR_IFU$weightIFU 

dfa_IFR_IFU_Actual <- merge(x=dummydf,y=dfa_IFR_IFU, by = c("date_month"),all = TRUE)

dfa_IFR_IFU_Actual[is.na(dfa_IFR_IFU_Actual)] <- 0

dfa_IFR_IFU_Actual <- select(dfa_IFR_IFU_Actual ,date_month, totalActual)

dfa_IFR_IFU_Actual <- dfa_IFR_IFU_Actual %>%
  mutate(totalRunningActual = cumsum(totalActual))

dfa_IFR_IFU_Actual <- select(dfa_IFR_IFU_Actual ,date_month, totalRunningActual)
```

## Merging three final dataframes

```{r}
df_final <- merge(x=dfp_IFR_IFU_planned,y=dff_IFR_IFU_Forecast, by = c("date_month"),all = TRUE)
df_final <- merge(x=df_final,y=dfa_IFR_IFU_Actual, by = c("date_month"),all = TRUE)
```

## Plot

```{r}
library(ggplot2)


ggplot(data = df_final) +
  geom_line(mapping = aes(x = date_month, y = totalRunningPLan, group = 1, color = "Plan")) +
  geom_point(mapping = aes(x = date_month, y = totalRunningPLan, group = 1, color = "Plan")) +
  geom_line(mapping = aes(x = date_month, y = totalRunningForecast, group = 1, color = "Forecast")) +
  geom_point(mapping = aes(x = date_month, y = totalRunningForecast, group = 1, color = "Forecast")) +
  geom_line(mapping = aes(x = date_month, y = totalRunningActual, group = 1, color = "Actual")) +
  geom_point(mapping = aes(x = date_month, y = totalRunningActual, group = 1, color = "Actual")) +
  scale_x_discrete(guide = guide_axis(check.overlap = TRUE)) +
  scale_color_manual(values = c("Plan" = "blue", "Forecast" = "orange", "Actual" = "red")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

```


